Figures to insert in text

### 2018-02-28 Chapters/Chapter02.tex
Merge.
SDM Applications Classification
SDM Classified application

\section{Results (i): Framework Validation}

@@

\section{Results (ii): Performance}

@@

\section{Results (iii): Noise filtering application}

We developed a noise filter using a SDM.

\section{Results (iv): Supervised classification application}

\section{Results (v): The possibility of unsupervised reinforcement learning}

\section{Results (vi): Information theoretical write operation}

@@

>>>>

\chapter{Results (i): Framework Validation}

@@

\chapter{Results (ii): Performance}

@@

\input{./Chapters/sdm-applications.tex}

\chapter{Results (vi): Information theoretical write operation}

@@

Future work: classification with context using sequences --- for words instead of only letters.
